---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SAI

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

Save time and effort by using SAI to clean and standardise your data. The SAI package is your AI assistant that contain a collection of functions to help you with your data cleaning tasks.

## Installation

You can install the development version of SAI like so:

``` r
# install.packages("pak")
pak::pak("emitanaka/SAI")
```

You will also need to install Ollama and one of the models, such as `r SAI::sai_get_option("model")` (the default for the SAI package). You can do this by running the following command in your terminal:

```bash
ollama pull llama3.1:8b
```



## Example


```{r}
library(SAI)
```

### Correcting order of levels for ordinal variables

The levels of categorical variables by default are ordered alphabetically. This can be problematic when the levels have a natural order.

```{r}
factor(likerts$likert1)
```

A correct order may need to be manually specified like below, but it can be a tedious task.

```{r}
factor(likerts$likert1, 
       levels = c("Strongly Disagree", "Disagree", "Somewhat Disagree", "Neutral", "Somewhat Agree", "Agree", "Strongly Agree")) 
```

The `sai_fct_reorder()` function will try to reorder the levels of the factor in a meaningful way _automatically_ using a large language model. 

```{r}
sai_fct_reorder(likerts$likert1) |> levels()
```

### Large language model

The default large language model is shown below.

```{r}
sai_get_option("model")
```

You can change the model to another one (provided that it is available in your system) like so:

```{r}
#| eval: false
sai_set_option("model", "llama3.1:1b")
```

Tiny models (1b) are faster but less accurate. It is not recommended to use them for important tasks.

### Categorise text

Some categorical variables can have simple typos or alternative representations. For example below we have UK written also as "United Kingdom". 


```{r}
messy$country
```

While you can manually fix this, again, this can be tedious. We can map this automatically using `sai_fct_match()`

```{r}
sai_fct_match(messy$country, levels = c("UK", "USA", "Canada", "Australia", "NZ"))
```

The function actucally works to match a continent as well! Let's use `sai_lvl_match()` to more easily see the conversion on the levels alone.


```{r}
sai_lvl_match(messy$country, levels = c("Asia", "Europe", "North America", "Oceania", "South America"))
```


### Translate

The `sai_translate()` function can be used to translate text to another language (default English). 

```{r}
sai_translate(c("猿も木から落ちる", "你好"))
```

